### 2017-07-17 main.tex
Remove author contributions. Revert subsubsection.

% PLOS wants \paragraph for some reason...
\renewcommand{\subsubsection}[1]{\paragraph{#1}}

@@

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
%\Yinyang These authors contributed equally to this work.
Author \textsuperscript{a}~contributed the original MATLAB and LabVIEW implementations and most of the manuscript.
\textsuperscript{b}~contributed the Swift implementation and its description herein, helped debug the training code, and measured the timing for most of the detectors.
\textsuperscript{c}~wrote several types of filter-bank software against which we compared, made suggestions for the neural network detector, and reformatted the MATLAB code for distribution.
\textsuperscript{d}~provided a stream of suggested techniques, metrics, and goals.

@@

\subsection{Training a detector}

@@

\begin{figure}
  % Width 10, height 4, font 100%
  \includegraphics[width=\textwidth]{Fig3}
  %\includegraphics[width=\textwidth]{accuracies-2hidden}

>>>>

% PLOS wants \paragraph for some reason...
%\renewcommand{\subsubsection}[1]{\paragraph{#1}}

@@

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
%\Yinyang These authors contributed equally to this work.

%Author \textsuperscript{a}~contributed the original MATLAB and LabVIEW %implementations and most of the manuscript.
%\textsuperscript{b}~contributed the Swift implementation and its description herein, %helped debug the training code, and measured the timing for most of the detectors.
%textsuperscript{c}~wrote several types of filter-bank software against which we %compared, made suggestions for the neural network detector, and reformatted the %MATLAB code for distribution.
%\textsuperscript{d}~provided a stream of suggested techniques, metrics, and goals.

@@

\subsection{Learning a detector}

@@

\begin{figure}
  % Width 8, height 3, font 120%
  \includegraphics[width=\textwidth]{Fig3}
  %\includegraphics[width=\textwidth]{accuracies-2hidden}
